%!TeX program = xelatex
\documentclass{article}

\usepackage{amsfonts}
\usepackage[all]{xy}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{mathrsfs}
\usepackage{amsthm}
\usepackage{enumerate}
\usepackage[hidelinks]{hyperref}
\usepackage{ulem}
\usepackage{tikz}  
\usetikzlibrary{arrows.meta}%画箭头用的包

\usepackage{geometry}
\geometry{a4paper,left=2cm,right=2cm,top=2cm,bottom=2cm}

\newtheorem{defn}{Definition}[section]
\newtheorem{prop}[defn]{Proposition}
\newtheorem{lem}[defn]{Lemma}
\newtheorem{thm}[defn]{Theorem}
\newtheorem{cor}[defn]{Corollary}
\newtheorem{rmk}[defn]{Remark}
\newtheorem{fact}[defn]{Fact}
\newtheorem{problem}{Problem}
\newtheorem*{ques}{Question}

\setcounter{section}{0}

\title{Lecture 4}
\author{wyz}
\date{\today}

\begin{document}

  \maketitle
  % \tableofcontents
  % \newpage
  \textbf{Special termination, Existence of Minimal model, Existence of Flips}
\section{Special termination}
Recall

\begin{thm}[Special termination of MMP with scaling]
  In above theorem setting, any $(K_{X}+B)$-MMP with scaling of  $B'-B$ is isomorphism along  $\left\lfloor B \right\rfloor $ after finitely many steps.
\end{thm}
  And  Exist of flip $_n$ + MMP with scaling Termination $_{n-1}$ $\implies$ Specila termination $_n$ 

Let $f:(X,B)\to S$ with BCHM conditiaion, and  $K_{X}+B'$ is nef over  $S$ for some $B\leqslant B'$. Run $K_{X}+B$-MMP with scaling of $B'-B$, then assume there is a sequence of flips:
\[
  (X,B)\dashrightarrow (X_{1},B_{1}) \dashrightarrow \cdots (X_{m},B_{m})  \overset{\alpha_{m}}{\dashrightarrow } \cdots
\]
then $\operatorname{Exc}\alpha_{m} \cap \left\lfloor B_{m} \right\rfloor = \emptyset$.
\textbf{remark:}Therefore Special termination implies PL flips terminate.
\subsection{Idea}
Let $Z \subset \left\lfloor B \right\rfloor$ prime divisor, then $(K_{X}+B)|_{Z}=K_{Z}+B_{Z}$ and is dlt. Then the MMP above induces 
\[
  (Z,B_{Z})\dashrightarrow (Z_{1},B_{Z,1}) \dashrightarrow \cdots (Z_{m},B_{Z,m}) \dashrightarrow \cdots
\]
If this is a MMP with scaling, then this ends. But this is not. Problems:
\begin{enumerate}
  \item $Z_{i}$ may not $\mathbb{Q}$-factorial
    \item  $Z_{i}\dashrightarrow Z_{i+1}$ may extract diviosrs
\end{enumerate}
Solutions:
\begin{enumerate}
  \item Show that$Z_{i}\dashrightarrow Z_{i+1}$ is contraction for $i\gg 0$
\item  take model$Z'_{i}$ of  $Z_{i}$ is MMP sequence.
\end{enumerate}
\begin{enumerate}[Step1]
  \item we may assume that $Z=\left\lfloor B \right\rfloor$. Then we have $K_{Z_{m}}+B_{Z,m}$ is klt. Let $I =\operatorname{Coeff} B_{i}$, then 

\textbf{Fact}: 
\[
  \operatorname{Coeff}B_{Z,m} \in \Sigma= \{ x \in [0,1]: x=1 - \frac{1}{r}+\sum \frac{m_{i}b_{i}}{r} , b_{i} \in I\} 
\]
Then $\Sigma$ infinite but $\Sigma \cap [0,1-\epsilon]$ is finite for any $0<\epsilon<1$.

If $Z_{i}\dashrightarrow Z_{i+1}$ extract a divisor $P$ , then 

\item  Lift to MMP. First take a $\mathbb{Q}$-factorialization of  $Z_{0}'\to Z_{0}$. (This is impled by MMP). Then run $(Z'_{0},B_{Z'_{0}}$-MMP over $Z_{0}$ with scaling of any ample diviosr, and end with minimal model $(Z'_{1},B_{Z'_1})$, and a natural map $(Z'_{1},B_{Z'_1})\to(Z_{1},B_{Z_{1}}$.

  Continue this process and  
  \[
    (Z',B_{Z'})\dashrightarrow (Z'_{1},B_{Z',1}) \dashrightarrow \cdots (Z'_{m},B_{Z',m}) \dashrightarrow \cdots
  \]
 this is MMP with scaling and terminates. 
\end{enumerate}
\section{Existence of minimal model}
   Exist of PL n + SpT n + NV $(X,B)$ n  $\implies$ Exist of minimal model for $(X,B)$ n

   Note that (Exist PL n +SpT n $\implies$ Exit of flip) is implied by above.

By Nonvanshing, we have $K_{X}+B \equiv_{S} D\geqslant 0$. If $\operatorname{Supp}D \subset \operatorname{Supp}\left\lfloor B \right\rfloor$, then the MMP is PL flips, and is done. However this doesnot hold.

\begin{enumerate}[Step0]
  \item we may assume $(X,B+D=\sum b_{i}B_{i}+\sum d_{i}D_{i})$ log smooth. 
\end{enumerate}
\end{document}
