%!TeX program = xelatex
\documentclass{article}

\usepackage{amsfonts}
\usepackage[all]{xy}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{mathrsfs}
\usepackage{amsthm}
\usepackage{enumerate}
\usepackage[hidelinks]{hyperref}
\usepackage{ulem}
\usepackage{tikz}  
\usetikzlibrary{arrows.meta}%画箭头用的包

\usepackage{geometry}
\geometry{a4paper,left=2cm,right=2cm,top=2cm,bottom=2cm}

\newtheorem{defn}{Definition}[section]
\newtheorem{prop}[defn]{Proposition}
\newtheorem{lem}[defn]{Lemma}
\newtheorem{thm}[defn]{Theorem}
\newtheorem{cor}[defn]{Corollary}
\newtheorem{rmk}[defn]{Remark}
\newtheorem{fact}[defn]{Fact}
\newtheorem{problem}{Problem}
\newtheorem*{ques}{Question}

\setcounter{section}{0}

\title{Lecture 3: PL flips}
\author{wyz}
\date{\today}

\begin{document}
  \maketitle
  % \tableofcontents
  % \newpage
\textbf{Existence and Finiteness of minimal model $(n-1)$ implies Exitence of PL filps$(n)$}: By Hacon-McKovenen shokuov and Extension thm. Reference: Kawamata book, section 3.2.1 and 3.2.2. and This is the theorem 3.2.1 in this book.

Recall  pl flip: $(X,B)$ is $\mathbb{Q}$-factorial dlt, a small flipping 
\[
  \xymatrix{
    X,B\ar[rd] \ar[rr] & & X^+,B^+\ar[ld] \\
    & S &
  }
\]
such that $ -\left\lfloor B \right\rfloor$ is ample over $S$.
WMA 
\begin{itemize}
  \item $B$ is $\mathbb{Q}$-divisor
  \item $\left\lfloor B \right\rfloor=Y$ is prime divisor. Since $\rho(X/S)= q$. And  $Y \to f(Y)$ is birational.
\end{itemize}
Note that Flip exits iff 
\[
  R(X/S,K_{X+B})
\]
is finite generated $\mathcal{Q}_{S}$-algebra. and we may assume $S$ is affine.

\textbf{adjunction}: $K_{X}+B|_{Y}=K_{Y}+B_{Y}$. and is klt.
we have restricton map
\[
  \phi:R(X/S,K_{X}+B) \to R(Y/S,K_{Y}+B_{Y})
\]
If  $\phi$ is surjectivem then $R(Y/S,K_{Y}+B_{Y})$ finite generated implies $R(X/S,K_{X}+B)$ finite generated.

\textbf{Claim}: $R(X/S,K_{X}+B)$ finite generated iff $\operatorname{Im}(\phi) \subset R(Y/S,K_{Y}+B_{Y})$ is finite generated $\mathcal{O}_{S}$-algebra. This is left as an excerise.
\begin{proof}
  $m_{0}(K_{X}+B)\sim _{S}m_{1}Y $ then 
\begin{itemize}
  \item $R(X/S,K_{X}+B)$ finite generated 
  \item iff $\oplus f_*\mathcal{O}_{X}(mm_0(K_{X}+B))$ f.g.
  \item iff $\oplus f_*\mathcal{O}_{X}(mm_1(Y))$ f.g.
\end{itemize}
ETS:  
\[
  \oplus \operatorname{Im}\left(H^{0}\left(X,mm_{0}\left(K_{X}+B\right)\right)\to H^{0}\left(Y,mm_{0}\left(K_{Y}+B_{Y}\right)\right)\right)
\]
is finitely generated
\begin{enumerate}[Step1]
  \item construct $\mu_{m}: X_{m}\to X$ birational such that 
    \begin{itemize}
      \item $\mu_{m}^*(K_{X}+B)=K_{X_{m}}+B_{m}$
      \item $Y'\cong Y_{m}'=\mu^{-1}_{m}Y$ independent on $m$
      \item $Y' \leqslant B_{m}' \leqslant  B_{m}^+$
      \item $H^0\left(mm_{0}\left(K_{X}+B\right)\right)\cong H^0(mm_{0}(K_{X_{m}}+B_{m}^+)) \cong H^0\left(mm_{0}\left(K_{X_{m}}+B_{m}'\right)\right) $
      \item $K_{X_{m}}B_{m}' =: K_{Y'}+B_{Y',m}$ klt pair;
      \item $m_{1}B_{Y',m_{1}}+m_{2}B_{Y',m_{2}}\leqslant \left(m_{1}+m_{2}\right)B_{Y',m_{1}+m_{2}}$
      \item $B_{Y'}:= \lim_{m \to \infty} B_{Y',m} $, then $(Y',B_{Y'})$ is klt.
    \end{itemize}
  This is Proposition 3.2.5 in Kawamata's book.
\end{enumerate}
\textbf{Goal:} $B_{Y',m}=B_{Y}$, for $m \gg 0$.
Using Induction assumption: finiteness of minimal models. There is common minimal model for pairs $(Y',B_{Y',m})$
\end{proof}
\end{document}
